What's hot and what's not:\\Windowed developer topic analysis

### 2009-06-24 lda-paper.tex
another change

\usepackage[usenames]{color}
\definecolor{changecolor1}{rgb}{0.5,0.3,0.08} 
\definecolor{changecolor2}{rgb}{0.3,0.08,0.45} 
\definecolor{changecolor3}{rgb}{0.3,0.45,0.45} 
\definecolor{changecolor4}{rgb}{0.0,0.3,0.0} 
\newcommand{\hl}[1]{{\color{changecolor1} #1 }}
\newcommand{\hla}[1]{{\color{changecolor2} #1 }}
\newcommand{\hlc}[1]{{\color{changecolor3} #1 }}
\newcommand{\hld}[1]{{\color{changecolor4} #1 }}

@@

\hdb{
Topic analysis extracts independant word distributions (topics) from
documents (commit log comments).
Ideally these extracted topics }
correlate with actual development topics that the developers discussed
during the development of the software project. 
Topic analysis often allows for a single document, such as a commit
\hlb{
message, to be related to multiple topics. Documents represented as a mixture of topics maps well to commits
}
\hla{
to source code, which often have more than one purpose.  A topic
represents both a word distribution and a group of commit log comments
that are related to each other by their content.  In this case a topic
is a set of tokens extracted from commit messages found within a
projects source control system (SCS). 
}

@@

\hlb{
We want to see topics that are unique to a
certain time period, displayed across the time axis.
Figure \ref{fig:lda} illustrates the kind of visualization we want to
automatically generate. } Those topics that
recur, or occur over a larger period are plotted continuously. In our
example we have titled each topic with a word drawn from its
word distribution.  
\hdb{
Given a visualization, such as Figure \ref{fig:lda}, topic
analysis can aid in partitioning a project's time-line into periods of
developer focus.
}
By breaking apart an iteration into sets of topics
and trends (topics that recur), we may be able to recognize the
underlying software development process and maintenance tasks from these
commits.

@@

\shrinkit
\SubSection{Visualization}
\shrinkit
%       1. [ ] need the visualizer
\hdb{ Visualization is an integral part of our topics analysis which
  allows us to quickly explore the topics and trends of a project.
  Visualization provides us with a framework that allows us to
  visually answer many questions about: the spread of topics, how many
  topics were independant per period, what the repeating trends were,
  if the trends dominated or did local topics dominate, how continuous
  trends were, and what the topic text in topic, trend, or period was.
  Since we have multiple questions to answer we have multiple
  visualization, described within this section, that help answer
  different questions.  }

@@

\hdb{
The \emph{trend-time-line} (Figure \ref{fig:trendtimeline})
attempts to show a summary of trends seperated from single topics. This view shows how a trend persists across time, which aids time-wise analysis of trends.
}
The \emph{trend-time-line} displays repeating trends more clearly by
dedicating a horizontal line for trend segments belonging to one
trend. Therefore if a trend contains discontinuous segments then
the segments appear on the same line.  However, the least common
trends need to be pruned away or the view will be very long. 
Thus the \emph{trend-time-line} view is used to analyze trends across time.

\hdb{ The \emph{trend-histogram} (Figure \ref{fig:histogram}) attempts
  to show a count of how often a trend reoccurs and how many topics
  are related to a trend. It is meant to show the distribution of
  trends by their size in topics and time-span.  } The
\emph{trend-histogram} superficially resembles the trend-time-line.
However, in this view the trends are plotted together by stacking to
the left of their row, thus time information is lost.  The trends are
ordered by the number of topics in the trend.  The trend-histogram
shows the count of instances of a trend and thus indicates which
trends occur the most. Unfortunately due to the large number of topics
(approximately $N$ topics multiplied by $M$ periods), given the
allotted space, it is often best to crop off the trends with only one
topic ($1\%$ to $10\%$ of the total topics), otherwise the tail is
long. \hdb{ The \emph{trend-histogram} summarizes the distribution of
trends ordered by size. }

\hdb{ All of these visualization combine to enable an analysis of
  trends and topics. Some views like the \emph{compact-trend-view}
  enable an analysis of local topics while the \emph{trend-histogram}
  and \emph{trend-time-line} focus more on trends. We used these
  visualizations to analyze the database systems that we discuss in
  the following results section.  }

>>>>

\usepackage[usenames]{color}
\definecolor{changecolor1}{rgb}{0.5,0.3,0.08} 
\definecolor{changecolor2}{rgb}{0.3,0.08,0.45} 
\definecolor{changecolor3}{rgb}{0.3,0.45,0.45} 
\definecolor{changecolor4}{rgb}{0.0,0.3,0.0} 
\newcommand{\hl}[1]{{\color{changecolor1} #1 }}
\newcommand{\hla}[1]{{\color{changecolor2} #1 }}
\newcommand{\hlb}[1]{{\color{changecolor3} #1 }}
\newcommand{\hlc}[1]{{\color{changecolor4} #1 }}

@@

\hla{
Topic analysis extracts independant word distributions (topics) from
documents (commit log comments).
Ideally these extracted topics }
correlate with actual development topics that the developers discussed
during the development of the software project. 
Topic analysis often allows for a single document, such as a commit
\hlb{
message, to be related to multiple topics. Documents represented as a mixture of topics maps well to commits
}
\hla{
to source code, which often have more than one purpose.  A topic
represents both a word distribution and a group of commit log comments
that are related to each other by their content.  In this case a topic
is a set of tokens extracted from commit messages found within a
projects source control system (SCS). 
}

@@

\hlb{
We want to see topics that are unique to a
certain time period, displayed across the time axis.
Figure \ref{fig:lda} illustrates the kind of visualization we want to
automatically generate. } Those topics that
recur, or occur over a larger period are plotted continuously. In our
example we have titled each topic with a word drawn from its
word distribution.  
\hla{
Given a visualization, such as Figure \ref{fig:lda}, topic
analysis can aid in partitioning a project's time-line into periods of
developer focus.
}
By breaking apart an iteration into sets of topics
and trends (topics that recur), we may be able to recognize the
underlying software development process and maintenance tasks from these
commits.

@@

\shrinkit
\SubSection{Visualization}
\shrinkit
%       1. [ ] need the visualizer
\hla{ Visualization is an integral part of our topics analysis which
  allows us to quickly explore the topics and trends of a project.
  Visualization provides us with a framework that allows us to
  visually answer many questions about: the spread of topics, how many
  topics were independant per period, what the repeating trends were,
  if the trends dominated or did local topics dominate, how continuous
  trends were, and what the topic text in topic, trend, or period was.
  Since we have multiple questions to answer we have multiple
  visualization, described within this section, that help answer
  different questions.  }

@@

\hla{
The \emph{trend-time-line} (Figure \ref{fig:trendtimeline})
attempts to show a summary of trends seperated from single topics. This view shows how a trend persists across time, which aids time-wise analysis of trends.
}
The \emph{trend-time-line} displays repeating trends more clearly by
dedicating a horizontal line for trend segments belonging to one
trend. Therefore if a trend contains discontinuous segments then
the segments appear on the same line.  However, the least common
trends need to be pruned away or the view will be very long. 
Thus the \emph{trend-time-line} view is used to analyze trends across time.

\hla{ The \emph{trend-histogram} (Figure \ref{fig:histogram}) attempts
  to show a count of how often a trend reoccurs and how many topics
  are related to a trend. It is meant to show the distribution of
  trends by their size in topics and time-span.  } The
\emph{trend-histogram} superficially resembles the trend-time-line.
However, in this view the trends are plotted together by stacking to
the left of their row, thus time information is lost.  The trends are
ordered by the number of topics in the trend.  The trend-histogram
shows the count of instances of a trend and thus indicates which
trends occur the most. Unfortunately due to the large number of topics
(approximately $N$ topics multiplied by $M$ periods), given the
allotted space, it is often best to crop off the trends with only one
topic ($1\%$ to $10\%$ of the total topics), otherwise the tail is
long. \hla{ The \emph{trend-histogram} summarizes the distribution of
trends ordered by size. }

\hla{ All of these visualization combine to enable an analysis of
  trends and topics. Some views like the \emph{compact-trend-view}
  enable an analysis of local topics while the \emph{trend-histogram}
  and \emph{trend-time-line} focus more on trends. We used these
  visualizations to analyze the database systems that we discuss in
  the following results section.  }
